User Preferences in Graphical and Textual Interfaces for Kubernetes

### 2021-08-19 Draft.tex
some spellcheck

\section{Evaluation Methodology}
\subsection{Low Level User Interactions}
A challenge we faced was in deciding what metrics to use to compare these tools. We sought to use a WhatPulse to measure physical user interaction frequencies and produce mouse movement heatmaps, however we observed errors in the numbers and decided not to use it \cite{}. Furthermore, to what extent do heatmaps let us compare between tools with different input methods? Heatmaps could be a good metric for A/B testing, however, they would be a poor metric for comparing different tools. We assume that these tools are already well designed and instead seek to study the limits that exist within the steady state of design and learning. These modalities will have certain limits and we seek to understand what are they as is to determine how we can improve them.

Wall clock time is easy to measure and is objective, however, across these tools isn’t really comparable because of the user variance we observed in the participant workflows. For example, one participant used the "Topology" view to access the logs for each deployment's pods (shown in Figure X) while other participants used the list of pods found in the "Project Inventory" to access the logs (shown in Figure X). User preference is a better metric, however, it may be too subjective. For example, knowing people prefer a CLI for certain tasks doesn’t help to improve the browser console for those tasks. Therefore, to support the qualitative data gathered in our surveys and study sessions, we also collected low level user interaction data, specifically user input types (keys, clicks, and mouse movements) and how frequently the participant used each user input type in completing the task on both tool interfaces.

@@

Furthermore, 
Regular expressions were also used to create shortened descriptions of the patterns of input types used to complete the task with each tool. Table X provides a list of the regular expressions participants used to complete the task with each tool. 
\subsection{Interpretation}
\subsubsection{Exhaustion}
In support of the qualitative data gathered from the surveys on participants' perceived cognitive load, we collect the user input frequencies as a measure of exhaustion due to the total number of interactions required to complete the task. These frequencies are shown for each participant in Tables X-X.
\subsubsection{Dissonance}
To further support the qualitative data gathered from the surveys on participants' perceived cognitive load, we kept track of the specific commands participants used as well as the inputs that make up those commands and patterns of switching between different inputs as a measure of dissonance due to the number of times the participant had to task switch to complete the task.

>>>>

\section{Evaluation Methodology}
\subsection{Low Level User Interactions}
A challenge we faced was in deciding what metrics to use to compare these tools. We sought to use WhatPulse to measure physical user interaction frequencies and produce mouse movement heatmaps, however we observed errors in the numbers and decided not to use it \cite{}. Furthermore, to what extent do heatmaps let us compare between tools with different input methods? Heatmaps could be a good metric for A/B testing, however, they would be a poor metric for comparing different tools. We assume that these tools are already well designed and instead seek to study the limits that exist within the steady state of design and learning. These modalities will have certain limits and we seek to understand what are they as is to determine how we can improve them.

Wall clock time is easy to measure and is objective, however, across these tools isn’t really comparable because of the user variance we observed in participant workflows. For example, one participant used the "Topology" view to access the logs for each deployment's pods (shown in Figure X) while other participants used the list of pods found in the "Project Inventory" to access the logs (shown in Figure X). User preference is a better metric, however, it may be too subjective. For example, knowing people prefer a CLI for certain tasks doesn’t help to improve the browser console for those tasks. Therefore, to support the qualitative data gathered in our surveys and study sessions, we also collected low level user interaction data, specifically user input types (keys, clicks, and mouse movements) and how frequently the participant used each user input type in completing the task on both tool interfaces.

@@

Regular expressions were also used to create shortened descriptions of the patterns of input types used to complete the task with each tool. Table X provides a list of the regular expressions participants used to complete the task with each tool.

\subsection{Interpretation}
\subsubsection{Exhaustion}
In support of the qualitative data gathered from the surveys on participants' perceived cognitive load, we collect the user input frequencies as a measure of exhaustion due to the total number of interactions required to complete the task. These frequencies are shown for each participant in Tables X-X.
\subsubsection{Dissonance}
To further support the qualitative data gathered from the surveys on participants' perceived cognitive load, we kept track of the specific commands participants used as well as the inputs that make up those commands and patterns of switching between different inputs as a measure of dissonance due to the number of times the participant had to task switch to complete the task.
